A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}

### 2021-09-29 paper.tex
Work in progress
Proposal improvement.

Our main inspiration for this algorithm was born from the study and observation
of nature, where many successful optimization algorithms have previously found
their own. Our focus was not on a single animal species but all of them, using
general abstraction to identify what those species have in common. Some
questions in our train of thought were:

\begin{description}  % When enumerating with description, bullet alternatives: cdot, bullet, ast
    \item[$\cdot$] How does nature work?
    \item[$\cdot$] Is evolution real?
    \item[$\cdot$] How do we enforce natural selection in evolution?
    \item[$\cdot$] What is the role of the attraction between couples on reproduction?
    \item[$\cdot$] How much of a factor is the attraction's role in the evolution of the species?
    \item[$\cdot$] What is the role of death in all of this?
    \item[$\cdot$] How much of an impact does death have on the evolution of a species?
    \item[$\cdot$] How do we include those ideas into our algorithm?
\end{description}

>>>>

Our main inspiration for this algorithm was born from the study and observation
of nature, where many successful optimization algorithms have previously found
their own. Our focus was not on a single animal species but all of them, using
general abstraction to identify what those species have in common.

Some questions in our train of thought were: How does nature work? Is evolution
real? How do we enforce natural selection in evolution? What is the role of the
attraction between couples on reproduction? How much of a factor is the
attraction's role in the evolution of the species? What is the role of death in
all of this? How much of an impact does death have on the evolution of a
species? How do we include those ideas into our algorithm?
